### 2023-08-23 documents/config/cariban_language_names.tex
fix abbrevs & lg names

\usepackage{xspace}
\providecommand{\apalai}{Apalaí\xspace}
\DeclareAcronym{apa_lg}{short=apa,long=Apalaí,short-format=\scshape}
\providecommand{\trio}{Tiriyó\xspace}
\DeclareAcronym{tri_lg}{short=tri,long=Tiriyó,short-format=\scshape}
\providecommand{\hixka}{Hixkaryána\xspace}
\DeclareAcronym{hix_lg}{short=hix,long=Hixkaryána,short-format=\scshape}
\providecommand{\panare}{Panare\xspace}
\DeclareAcronym{pan_lg}{short=pan,long=Panare,short-format=\scshape}
\providecommand{\macushi}{Macushi\xspace}
\DeclareAcronym{mac_lg}{short=mac,long=Macushi,short-format=\scshape}
\providecommand{\waimiri}{Waimiri-Atroari\xspace}
\DeclareAcronym{wmr_lg}{short=wmr,long=Waimiri-Atroari,short-format=\scshape}
\providecommand{\maqui}{Ye'kwana\xspace}
\DeclareAcronym{mak_lg}{short=mak,long=Ye'kwana,short-format=\scshape}
\providecommand{\waiwai}{Waiwai\xspace}
\DeclareAcronym{wai_lg}{short=wai,long=Waiwai,short-format=\scshape}
\providecommand{\wayana}{Wayana\xspace}
\DeclareAcronym{way_lg}{short=way,long=Wayana,short-format=\scshape}
\providecommand{\kalina}{Kari'ña\xspace}
\DeclareAcronym{kar_lg}{short=kar,long=Kari'ña,short-format=\scshape}
\providecommand{\ikpeng}{Ikpeng\xspace}
\DeclareAcronym{ikp_lg}{short=ikp,long=Ikpeng,short-format=\scshape}
\providecommand{\uxc}{Upper Xingu Carib\xspace}
\DeclareAcronym{uxc_lg}{short=uxc,long=Upper Xingu Carib,short-format=\scshape}
\providecommand{\arara}{Arara\xspace}
\DeclareAcronym{ara_lg}{short=ara,long=Arara,short-format=\scshape}
\providecommand{\ingariko}{Ingarikó\xspace}
\DeclareAcronym{ing_lg}{short=ing,long=Ingarikó,short-format=\scshape}
\providecommand{\pemon}{Pemón\xspace}
\DeclareAcronym{pem_lg}{short=pem,long=Pemón,short-format=\scshape}
\providecommand{\kapon}{Kapón\xspace}
\DeclareAcronym{kap_lg}{short=kap,long=Kapón,short-format=\scshape}
\providecommand{\kalapalo}{Kalapalo\xspace}
\DeclareAcronym{kal_lg}{short=kal,long=Kalapalo,short-format=\scshape}
\providecommand{\kuikuro}{Kuikuro\xspace}
\DeclareAcronym{kui_lg}{short=kui,long=Kuikuro,short-format=\scshape}
\providecommand{\yukpa}{Yukpa\xspace}
\DeclareAcronym{yuk_lg}{short=yuk,long=Yukpa,short-format=\scshape}
\providecommand{\carijo}{Carijona\xspace}
\DeclareAcronym{car_lg}{short=car,long=Carijona,short-format=\scshape}
\providecommand{\bakairi}{Bakairi\xspace}
\DeclareAcronym{bak_lg}{short=bak,long=Bakairi,short-format=\scshape}
\providecommand{\tamanaku}{†Tamanaku\xspace}
\DeclareAcronym{tam_lg}{short=tam,long=†Tamanaku,short-format=\scshape}
\providecommand{\kaxui}{Werikyana\xspace}
\DeclareAcronym{kax_lg}{short=kax,long=Werikyana,short-format=\scshape}
\providecommand{\akuriyo}{Akuriyó\xspace}
\DeclareAcronym{aku_lg}{short=aku,long=Akuriyó,short-format=\scshape}
\providecommand{\japreria}{Japreria\xspace}
\DeclareAcronym{jap_lg}{short=jap,long=Japreria,short-format=\scshape}
\providecommand{\kumana}{†Kumaná\xspace}
\DeclareAcronym{cum_lg}{short=cum,long=†Kumaná,short-format=\scshape}
\providecommand{\palmela}{†Palmela\xspace}
\DeclareAcronym{palm_lg}{short=palm,long=†Palmela,short-format=\scshape}
\providecommand{\piment}{†Pimenteira\xspace}
\DeclareAcronym{pime_lg}{short=pime,long=†Pimenteira,short-format=\scshape}
\providecommand{\arakaju}{†Arakaju\xspace}
\DeclareAcronym{arak_lg}{short=arak,long=†Arakaju,short-format=\scshape}
\providecommand{\pauxiana}{†Pauxiana\xspace}
\DeclareAcronym{pxan_lg}{short=pxan,long=†Pauxiana,short-format=\scshape}
\providecommand{\paravi}{†Paravilhana\xspace}
\DeclareAcronym{para_lg}{short=para,long=†Paravilhana,short-format=\scshape}
\providecommand{\bonari}{†Bonari\xspace}
\DeclareAcronym{bona_lg}{short=bona,long=†Bonari,short-format=\scshape}
\providecommand{\wayu}{†Wayumara\xspace}
\DeclareAcronym{wayu_lg}{short=wayu,long=†Wayumara,short-format=\scshape}
\providecommand{\apiaka}{†Apiaka-Tocantins\xspace}
\DeclareAcronym{apia_lg}{short=apia,long=†Apiaka-Tocantins,short-format=\scshape}
\providecommand{\opon}{†Opón-Carare\xspace}
\DeclareAcronym{opon_lg}{short=opon,long=†Opón-Carare,short-format=\scshape}
\providecommand{\pauxi}{†Pauxi\xspace}
\DeclareAcronym{paux_lg}{short=paux,long=†Pauxi,short-format=\scshape}
\providecommand{\sapara}{†Sapara\xspace}
\DeclareAcronym{sapa_lg}{short=sapa,long=†Sapara,short-format=\scshape}
\providecommand{\tiveri}{†Tiverighotto\xspace}
\DeclareAcronym{tive_lg}{short=tive,long=†Tiverighotto,short-format=\scshape}
\providecommand{\yao}{†Yao\xspace}
\DeclareAcronym{yao_lg}{short=yao,long=†Yao,short-format=\scshape}
\providecommand{\yaruma}{†Yarumá\xspace}
\DeclareAcronym{yaru_lg}{short=yaru,long=†Yarumá,short-format=\scshape}
\providecommand{\koyaima}{†Koyaima\xspace}
\DeclareAcronym{koya_lg}{short=koya,long=†Koyaima,short-format=\scshape}
\providecommand{\hiana}{†Hianakoto-Umawa\xspace}
\DeclareAcronym{hian_lg}{short=hian,long=†Hianakoto-Umawa,short-format=\scshape}
\providecommand{\saluma}{†Salumá\xspace}
\DeclareAcronym{salu_lg}{short=salu,long=†Salumá,short-format=\scshape}
\providecommand{\sikiana}{†Sikiana\xspace}
\DeclareAcronym{siku_lg}{short=siku,long=†Sikiana,short-format=\scshape}
\providecommand{\purukoto}{†Purukoto\xspace}
\DeclareAcronym{puru_lg}{short=puru,long=†Purukoto,short-format=\scshape}
\providecommand{\juma}{†Juma\xspace}
\DeclareAcronym{juma_lg}{short=juma,long=†Juma,short-format=\scshape}
\providecommand{\palenque}{†Palenque\xspace}
\DeclareAcronym{pale_lg}{short=pale,long=†Palenque,short-format=\scshape}
\providecommand{\parukoto}{†Parukoto\xspace}
\DeclareAcronym{paru_lg}{short=paru,long=†Parukoto,short-format=\scshape}
\providecommand{\urukue}{†Urukuena\xspace}
\DeclareAcronym{uruk_lg}{short=uruk,long=†Urukuena,short-format=\scshape}
\providecommand{\wayakule}{†Wayakulé\xspace}
\DeclareAcronym{waya_lg}{short=waya,long=†Wayakulé,short-format=\scshape}
\providecommand{\piritu}{†Píritu\xspace}
\DeclareAcronym{piri_lg}{short=piri,long=†Píritu,short-format=\scshape}
\providecommand{\guake}{†Guake\xspace}
\DeclareAcronym{guak_lg}{short=guak,long=†Guake,short-format=\scshape}
\providecommand{\macoita}{†Macoita\xspace}
\DeclareAcronym{mcta_lg}{short=mcta,long=†Macoita,short-format=\scshape}
\providecommand{\macoa}{†Macoa\xspace}
\DeclareAcronym{maco_lg}{short=maco,long=†Macoa,short-format=\scshape}
\providecommand{\chake}{†Chake\xspace}
\DeclareAcronym{chak_lg}{short=chak,long=†Chake,short-format=\scshape}
\providecommand{\chayma}{†Chayma\xspace}
\DeclareAcronym{chai_lg}{short=chai,long=†Chayma,short-format=\scshape}
\providecommand{\avarikoto}{†Avarikoto\xspace}
\DeclareAcronym{avar_lg}{short=avar,long=†Avarikoto,short-format=\scshape}
\providecommand{\tauli}{Taulipang\xspace}
\DeclareAcronym{tau_lg}{short=tau,long=Taulipang,short-format=\scshape}
\providecommand{\patamona}{Patamona\xspace}
\DeclareAcronym{pat_lg}{short=pat,long=Patamona,short-format=\scshape}
\providecommand{\arekuna}{Arekuna\xspace}
\DeclareAcronym{are_lg}{short=are,long=Arekuna,short-format=\scshape}
\providecommand{\kamara}{Kamarakoto\xspace}
\DeclareAcronym{kam_lg}{short=kam,long=Kamarakoto,short-format=\scshape}
\providecommand{\akawaio}{Akawaio\xspace}
\DeclareAcronym{aka_lg}{short=aka,long=Akawaio,short-format=\scshape}
\providecommand{\kumanagoto}{†Kumanagoto\xspace}
\DeclareAcronym{cgt_lg}{short=cgt,long=†Kumanagoto,short-format=\scshape}
\providecommand{\crichana}{†Crichana\xspace}
\DeclareAcronym{cric_lg}{short=cric,long=†Crichana,short-format=\scshape}
\providecommand{\mapoyo}{Mapoyo\xspace}
\DeclareAcronym{map_lg}{short=map,long=Mapoyo,short-format=\scshape}
\providecommand{\yawarana}{Yawarana\xspace}
\DeclareAcronym{yab_lg}{short=yab,long=Yawarana,short-format=\scshape}
\providecommand{\yawaperi}{†Jawaperi\xspace}
\DeclareAcronym{jawa_lg}{short=jawa,long=†Jawaperi,short-format=\scshape}
\providecommand{\pemono}{†Pémono\xspace}
\DeclareAcronym{pemo_lg}{short=pemo,long=†Pémono,short-format=\scshape}
\providecommand{\pianakoto}{†Pianakoto\xspace}
\DeclareAcronym{pian_lg}{short=pian,long=†Pianakoto,short-format=\scshape}
\providecommand{\PC}{Proto-Cariban\xspace}
\DeclareAcronym{pc_lg}{short=pc,long=Proto-Cariban,short-format=\scshape}
\providecommand{\arina}{†Arinakoto\xspace}
\DeclareAcronym{arin_lg}{short=arin,long=†Arinakoto,short-format=\scshape}
\providecommand{\kumayena}{†Kumayena\xspace}
\DeclareAcronym{kuma_lg}{short=kuma,long=†Kumayena,short-format=\scshape}
\providecommand{\tyrewuju}{Tyrewuju\xspace}
\DeclareAcronym{tyr_lg}{short=tyr,long=Tyrewuju,short-format=\scshape}
\providecommand{\dekwana}{De’kwana\xspace}
\DeclareAcronym{dek_lg}{short=dek,long=De’kwana,short-format=\scshape}
\providecommand{\dhekwana}{Dhe’kwana\xspace}
\DeclareAcronym{dhe_lg}{short=dhe,long=Dhe’kwana,short-format=\scshape}
\newcommand{\PPar}{Proto-Parukotoan\xspace}
\newcommand{\PPars}{\textsc{PPar}\xspace}
\newcommand{\PPem}{Proto-Pemongan\xspace}
\newcommand{\PPems}{\textsc{PPem}\xspace}
\newcommand{\PPek}{Proto-Pekodian\xspace}
\newcommand{\PPeks}{\textsc{PPek}\xspace}
\newcommand{\PPP}{Proto-Panare-Pemongan\xspace}
\newcommand{\PPPs}{\textsc{PPP}\xspace}
\newcommand{\PTir}{Proto-Tiriyoan\xspace}
\newcommand{\PTirs}{\textsc{PTir}\xspace}
\newcommand{\PWai}{Proto-Waiwaian\xspace}
\newcommand{\PWais}{\textsc{PWai}\xspace}
\newcommand{\PXin}{Proto-Xinguan\xspace}
\newcommand{\PXins}{\textsc{PXin}\xspace}
\newcommand{\PTar}{Proto-Taranoan\xspace}
\newcommand{\PTars}{\textsc{PTar}\xspace}
\newcommand{\yabmap}{\mapoyo-\yawarana}
\newcommand{\yabmaps}{\textsc{yab-map}\xspace}
\newcommand{\vzk}{Venezuelan \kalina}
\newcommand{\vzks}{\textsc{vzk}\xspace}
\newcommand{\esk}{Eastern Surinamese \kalina}
\newcommand{\esks}{\textsc{esk}\xspace}
\newcommand{\wsk}{Western Surinamese \kalina}
\newcommand{\wsks}{\textsc{wsk}\xspace}
\renewcommand{\lg}[1]{\acs*{#1_lg}}

>>>>

\usepackage{xspace}
\providecommand{\wbakairi}{Western Bakairi\xspace}
\providecommand{\ebakairi}{Eastern Bakairi\xspace}
\providecommand{\ingariko}{Ingarikó\xspace}
\providecommand{\akawaio}{Akawaio\xspace}
\providecommand{\patamona}{Patamona\xspace}
\providecommand{\yukpa}{Yukpa\xspace}
\providecommand{\japreria}{Japreria\xspace}
\providecommand{\carijo}{Karijona\xspace}
\providecommand{\mapoyo}{Mapoyo\xspace}
\providecommand{\yawarana}{Yawarana\xspace}
\providecommand{\panare}{Panare\xspace}
\providecommand{\maqui}{Ye'kwana\xspace}
\providecommand{\pemon}{Pemón\xspace}
\providecommand{\kapon}{Kapong\xspace}
\providecommand{\waimiri}{Waimiri-Atroari\xspace}
\providecommand{\macushi}{Macushi\xspace}
\providecommand{\waiwai}{Waiwai\xspace}
\providecommand{\hixka}{Hixkaryána\xspace}
\providecommand{\kaxui}{Werikyana\xspace}
\providecommand{\trio}{Tiriyó\xspace}
\providecommand{\akuriyo}{Akuriyó\xspace}
\providecommand{\apalai}{Apalaí\xspace}
\providecommand{\wayana}{Wayana\xspace}
\providecommand{\ikpeng}{Ikpeng\xspace}
\providecommand{\arara}{Arara\xspace}
\providecommand{\kalina}{Kari'ña\xspace}
\providecommand{\uxc}{Upper Xingu Carib\xspace}
\providecommand{\bakairi}{Bakairi\xspace}
\providecommand{\PC}{Proto-Cariban\xspace}
\providecommand{\PPar}{Proto-Parukotoan\xspace}
\providecommand{\PWai}{Proto-Waiwaian\xspace}
\providecommand{\PPek}{Proto-Pekodian\xspace}
\providecommand{\PXin}{Proto-Xinguan\xspace}
\providecommand{\PPP}{Proto-Pemong-Panare\xspace}
\providecommand{\PTar}{Proto-Taranoan\xspace}
\providecommand{\PTir}{Proto-Tiriyoan\xspace}

### 2023-08-23 documents/config/own_abbreviations.tex
latex compilation working again
fix abbrevs & lg names

\newGlossingAbbrev{inter}{interrogative}
\DeclareAcronym{tam}{short=TAM,long=Tense-Aspect-Mood,class=other}

>>>>

\DeclareAcronym{1}{short=1,long=first~person,short-format=\scshape}
\DeclareAcronym{1+2}{short=1+2,long=first~person~inclusive,short-format=\scshape}
\DeclareAcronym{1+3}{short=1+3,long=first~person~exclusive,short-format=\scshape}
\DeclareAcronym{2}{short=2,long=second~person,short-format=\scshape}
\DeclareAcronym{3}{short=3,long=third~person,short-format=\scshape}
\DeclareAcronym{a}{short=A,long=agent-like~argument~of~canonical~transitive~verb,short-format=\scshape}
\DeclareAcronym{agt}{short=agt,long=agent,short-format=\scshape}
\DeclareAcronym{ana}{short=ana,long=anaphoric,short-format=\scshape}
\DeclareAcronym{attrz}{short=attrz,long=attributivizer,short-format=\scshape}
\DeclareAcronym{caus}{short=caus,long=causative,short-format=\scshape}
\DeclareAcronym{cert}{short=cert,long=certainty,short-format=\scshape}
\DeclareAcronym{com}{short=com,long=comitative,short-format=\scshape}
\DeclareAcronym{cont}{short=cont,long=continuative,short-format=\scshape}
\DeclareAcronym{cor}{short=cor,long=coreference,short-format=\scshape}
\DeclareAcronym{dem}{short=dem,long=demonstrative,short-format=\scshape}
\DeclareAcronym{des}{short=des,long=desiderative,short-format=\scshape}
\DeclareAcronym{detrz}{short=detrz,long=detransitivizer,short-format=\scshape}
\DeclareAcronym{dub}{short=dub,long=dubitative,short-format=\scshape}
\DeclareAcronym{evid}{short=evid,long=evidentiality,short-format=\scshape}
\DeclareAcronym{frust}{short=frust,long=frustrative,short-format=\scshape}
\DeclareAcronym{hsy}{short=hsy,long=hearsay/indirect~evidentiality,short-format=\scshape}
\DeclareAcronym{imm}{short=imm,long=immentiate~past,short-format=\scshape}
\DeclareAcronym{imp}{short=imp,long=imperative,short-format=\scshape}
\DeclareAcronym{inan}{short=inan,long=inanimate,short-format=\scshape}
\DeclareAcronym{inf}{short=inf,long=infinitive,short-format=\scshape}
\DeclareAcronym{intr}{short=intr,long=intermediate~past,short-format=\scshape}
\DeclareAcronym{ints}{short=ints,long=intensifier,short-format=\scshape}
\DeclareAcronym{lk}{short=lk,long=linker,short-format=\scshape}
\DeclareAcronym{loc}{short=loc,long=locative,short-format=\scshape}
\DeclareAcronym{med}{short=med,long=medial,short-format=\scshape}
\DeclareAcronym{neg}{short=neg,long=negation,short-format=\scshape}
\DeclareAcronym{nmlz}{short=nmlz,long=nominalizer,short-format=\scshape}
\DeclareAcronym{npst}{short=npst,long=non-past,short-format=\scshape}
\DeclareAcronym{obl}{short=obl,long=oblique,short-format=\scshape}
\DeclareAcronym{p}{short=p,long=patient-like~argument~of~canonical~transitive~verb,short-format=\scshape}
\DeclareAcronym{pfv}{short=pfv,long=perfective,short-format=\scshape}
\DeclareAcronym{pl}{short=pl,long=plural,short-format=\scshape}
\DeclareAcronym{pro}{short=pro,long=pronoun,short-format=\scshape}
\DeclareAcronym{prs}{short=prs,long=present,short-format=\scshape}
\DeclareAcronym{pst}{short=pst,long=past,short-format=\scshape}
\DeclareAcronym{rec}{short=rec,long=recent~past,short-format=\scshape}
\DeclareAcronym{rem}{short=rem,long=remote~past,short-format=\scshape}
\DeclareAcronym{s}{short=s,long=single~argument~of~canonical~intransitive~verb,short-format=\scshape}
\DeclareAcronym{sa}{short=S\textsubscript{A},long=S~marked~like~A,short-format=\scshape}
\DeclareAcronym{sp}{short=S\textsubscript{P},long=S~marked~like~P,short-format=\scshape}
\DeclareAcronym{sap}{short=sap,long=speech~act~participant,short-format=\scshape}
\DeclareAcronym{sup}{short=sup,long=supine,short-format=\scshape}
\DeclareAcronym{tam}{short=TAM,long=tense-aspect-mood,short-format=\scshape}
\DeclareAcronym{tr}{short=tr,long=transitive,short-format=\scshape}
\DeclareAcronym{uncert}{short=uncert,long=uncertainty,short-format=\scshape}
\DeclareAcronym{inter}{short=inter,long=interrogative,short-format=\scshape}
\DeclareAcronym{int}{short=int,long=intermediate~past,short-format=\scshape}
\DeclareAcronym{all}{short=all,long=allative,short-format=\scshape}
\DeclareAcronym{dat}{short=dat,long=dative,short-format=\scshape}

### 2023-08-23 documents/floats/nominalizations.tex
regular verbs in data and docs
new approach to testing predictions from bybee's model
moved verb discussion to verbs section, fixed lingpy alignments, fixed map
rewriting and restructuring
fix abbrevs & lg names

\begin{tabular}[t]{@{}lll@{}}
\toprule
Language &                                         \gl{s_a_} &                                             \gl{s_p_} \\
\midrule
\kaxui  &       \obj{o-\emp{w-}ehurka-tpɨrɨ} \qu{your fall} &            \obj{o-onenmehɨ-tpɨrɨ} \qu{your waking up} \\
\arara  &        \obj{\emp{w-}orik-tubo} \qu{dancing place} &              \obj{ereŋmɨ-tpo} \qu{killing instrument} \\
\trio   &   \obj{ji-\emp{w-}əturu-to} \qu{(for) my talking} &              \obj{j-emamina-to} \qu{(for) my playing} \\
\wayana &          \obj{ɨ-\emp{w-}əturu-topo} \qu{my story} &        \obj{j-ɨnɨkɨ-topo} \qu{my object for sleeping} \\
\apalai &            \obj{j-epɨ-topo} \qu{my bathing place} &   \obj{j-enuru-topõ-pɨrɨ} \qu{the place of my birth} \\
\kalina &  \obj{a-\emp{w-}ekupi-rɨ} \qu{your taking a bath} &                  \obj{aj-ereʔna-∅} \qu{your fainting} \\
\panare &     \obj{j-\emp{u-}t͡ʃireema-n} \qu{their eating} &  \obj{tj-arunkampətɨ-n} \qu{his hair standing on end} \\
\bottomrule
\end{tabular}

>>>>

\begin{table}
\centering
\caption[Nominalizations of \gl{sa} and \gl{sp} verbs]{Nominalizations of \gl{sa} and \gl{sp} verbs \parencites[49, 74]{schuring2018kaxuyana}[97]{alves2017arara}[246]{triomeira1999}[130, 409]{wayanatavares2005}[90]{koehn1986apalai}[ner2-003]{koehns1994textos}[135, 392]{hoff1968carib}[390]{panarepayne2013}[23]{mattei1994diccionario}}
\label{tab:nominalizations}
\begin{tabular}[t]{@{}lll@{}}
\mytoprule
Language &                                         \gl{sa} &                                             \gl{sp} \\
\mymidrule
\kaxui  &       \obj{o-\emp{w-}ehurka-tpɨrɨ} \qu{your fall} &            \obj{o-onenmehɨ-tpɨrɨ} \qu{your waking up} \\
\arara  &        \obj{\emp{w-}orik-tubo} \qu{dancing place} &              \obj{ereŋmɨ-tpo} \qu{killing instrument} \\
\trio   &   \obj{ji-\emp{w-}əturu-to} \qu{(for) my talking} &              \obj{j-emamina-to} \qu{(for) my playing} \\
\wayana &          \obj{ɨ-\emp{w-}əturu-topo} \qu{my story} &        \obj{j-ɨnɨkɨ-topo} \qu{my object for sleeping} \\
\apalai &            \obj{j-epɨ-topo} \qu{my bathing place} &   \obj{j-enuru-topõ-pɨrɨ} \qu{the place of my birth} \\
\kalina &  \obj{a-\emp{w-}ekupi-rɨ} \qu{your taking a bath} &    \obj{aj-ereʔna-{\normalfont ∅}} \qu{your fainting} \\
\panare &     \obj{j-\emp{u-}t͡ʃireema-n} \qu{their eating} &  \obj{tj-arunkampətɨ-n} \qu{his hair standing on end} \\
\mybottomrule
\end{tabular}
\end{table}

### 2023-08-23 documents/floats/participles.tex
fix abbrevs & lg names

\begin{tabular}[t]{@{}lll@{}}
\toprule
Language &                               \gl{s_a_} &                        \gl{s_p_} \\
\midrule
\kaxui  &         \obj{t-ehurka-t͡ʃe} \qu{fallen} &       \obj{tɨ-jaʔ-so} \qu{burnt} \\
\arara  &         \obj{t-\emp{o-}ep-te} \qu{come} &      \obj{t-oregrum-te} \qu{sad} \\
\trio   &    \obj{tɨ-\emp{w-}əturu-e} \qu{talked} &       \obj{t-əpəə-se} \qu{tired} \\
\wayana &     \obj{tə-\emp{w-}epɨ-he} \qu{bathed} &    \obj{t-onopɨ-he} \qu{painted} \\
\apalai &  \obj{t-\emp{o-}erama-se} \qu{returned} &      \obj{t-anorɨ-se} \qu{dried} \\
\kalina &  \obj{tu-\emp{w-}oʔka-se} \qu{come out} &       \obj{t-okari-se} \qu{told} \\
\panare &  \obj{t-\emp{o-}tatɨhpə-se} \qu{wailed} &  \obj{tɨ-sɨrɨke-t͡ʃe} \qu{tired} \\
\bottomrule
\end{tabular}

>>>>

\begin{table}
\centering
\caption[Participles of \gl{sa} and \gl{sp} verbs]{Participles of \gl{sa} and \gl{sp} verbs \parencites[39]{schuring2018kaxuyana}[118, 207]{alves2017arara}[333-334]{triomeira1999}[400]{wayanatavares2005}[35]{koehn1986apalai}[kuruaz-154]{koehns1994textos}[430, 433]{hoff1968carib}[232, 244]{panarepayne2013}}
\label{tab:participles}
\begin{tabular}[t]{@{}lll@{}}
\mytoprule
Language &                               \gl{sa} &                        \gl{sp} \\
\mymidrule
\kaxui  &         \obj{t-ehurka-t͡ʃe} \qu{fallen} &       \obj{tɨ-jaʔ-so} \qu{burnt} \\
\arara  &         \obj{t-\emp{o-}ep-te} \qu{come} &      \obj{t-oregrum-te} \qu{sad} \\
\trio   &    \obj{tɨ-\emp{w-}əturu-e} \qu{talked} &       \obj{t-əpəə-se} \qu{tired} \\
\wayana &     \obj{tə-\emp{w-}epɨ-he} \qu{bathed} &    \obj{t-onopɨ-he} \qu{painted} \\
\apalai &        \obj{t-\emp{o-}ɨto-se} \qu{gone} &   \obj{t-ɨhto-se} \qu{gone down} \\
\kalina &  \obj{tu-\emp{w-}oʔka-se} \qu{come out} &       \obj{t-okari-se} \qu{told} \\
\panare &  \obj{t-\emp{o-}tatɨhpə-se} \qu{wailed} &  \obj{tɨ-sɨrɨke-t͡ʃe} \qu{tired} \\
\mybottomrule
\end{tabular}
\end{table}

### 2023-08-23 documents/floats/pekreg.tex
moved verb discussion to verbs section, fixed lingpy alignments, fixed map
rewriting and restructuring
a thousand small fixes
more data processing
fix abbrevs & lg names

\begin{table}
\centering
\caption[Regular Pekodian \gl{s_a_} verbs]{Regular Pekodian \gl{s_a_} verbs \parencites[4]{meira2003bakairi}[150]{alves2017arara}[52]{ikpengpacheco2001}}
\label{tab:pekreg}
\begin{tabular}[t]{@{}llll@{}}
\mytoprule
{} & \bakairi \qu{to go up} &         \arara \qu{to dance} &            \ikpeng \qu{to run} \\
\midrule
\gl{1}   &           \obj{k-əku-} &               \obj{k-origu-} &                \obj{k-aranme-} \\
\gl{2}   &           \obj{m-əku-} &               \obj{m-origu-} &                \obj{m-aranme-} \\
\gl{1+2} &         \obj{kɨd-əku-} &             \obj{kud-origu-} &               \obj{kw-aranme-} \\
\gl{3}   &           \obj{n-əku-} &  \obj{{\normalfont ∅}-origu} &  \obj{{\normalfont ∅}-aranme-} \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\centering
\caption[Regular Pekodian \gl{sa} verbs]{Regular Pekodian \gl{sa} verbs \parencites[4]{meira2003bakairi}[150]{alves2017arara}[52]{ikpengpacheco2001}}
\label{tab:pekreg}
\begin{tabular}[t]{@{}llll@{}}
\mytoprule
{} & \ebakairi \qu{to go up} &         \arara \qu{to dance} &            \ikpeng \qu{to run} \\
\mymidrule
\gl{1}   &            \obj{k-əku-} &               \obj{k-origu-} &                \obj{k-aranme-} \\
\gl{2}   &            \obj{m-əku-} &               \obj{m-origu-} &                \obj{m-aranme-} \\
\gl{1+2} &          \obj{kɨd-əku-} &             \obj{kud-origu-} &               \obj{kw-aranme-} \\
\gl{3}   &            \obj{n-əku-} &  \obj{{\normalfont ∅}-origu} &  \obj{{\normalfont ∅}-aranme-} \\
\mybottomrule
\end{tabular}
\end{table}

### 2023-08-23 documents/floats/ppekverbs.tex
more table fixes
fix abbrevs & lg names

\begin{table}
\centering
\caption[Verbs preserving \gl{1}\gl{s_a_} \rc{w-} in \PPek]{Verbs preserving \gl{1}\gl{s_a_} \rc{w-} in \PPek \parencites[153, 200]{alves2017arara}[42, 80, 139, 209]{ikpengpacheco2001}[129, 170]{meiraDBebakairi / pinto2022bakairi}[68]{ikpengpacheco1997}[4]{meira2003bakairi}[111]{pinto2022bakairi}{meiraDBebakairi}}
\label{tab:ppekverbs}
\begin{tabular}[t]{@{}lllll@{}}
\mytoprule
{} &          \PPek &          \arara &                       \ikpeng &             \ebakairi \\
\mymidrule
\qu{say}     &    \rc{wɨ-ge-} &    \obj{wɨ-ge-} &                   \obj{ɨ-ge-} &  \obj{u-gue- / u-ge-} \\
\qu{bathe}   &    \rc{w-ipɨ-} &    \obj{w-ibɨ-} &     \obj{{\normalfont ∅}-ip-} &            \obj{w-i-} \\
\qu{be-1}    &     \rc{w-ap-} &     \obj{w-ap-} &                             – &          \obj{w-awɨ-} \\
\qu{be-2}    &  \rc{w-et͡ʃi-} &  \obj{w-it͡ʃi-} &  \obj{{\normalfont ∅}-et͡ʃi-} &            \obj{w-i-} \\
\qu{come}    &    \rc{w-epɨ-} &    \obj{w-ebɨ-} &                 \obj{k-arep-} &         \obj{k-əewɨ-} \\
\qu{go down} &   \rc{w-ɨptə-} &                 &                               &                       \\
\qu{go}      &   \rc{w-ɨdən-} &    \obj{w-ɨdo-} &                 \obj{k-aran-} &           \obj{u-də-} \\
\mybottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\centering
\caption[Verbs preserving \gl{1}\gl{sa} \rc{w-} in \PPek]{Verbs preserving \gl{1}\gl{sa} \rc{w-} in \PPek \parencites[153, 200]{alves2017arara}[42, 80, 139, 209]{ikpengpacheco2001}[129, 170]{meiraDBebakairi / pinto2022bakairi}[68]{ikpengpacheco1997}[4]{meira2003bakairi}[111]{pinto2022bakairi}{meiraDBebakairi}}
\label{tab:ppekverbs}
\begin{tabular}[t]{@{}lllll@{}}
\mytoprule
{} &          \PPek &          \arara &                       \ikpeng &                   \ebakairi \\
\mymidrule
\qu{say}     &    \rc{wɨ-ge-} &    \obj{wɨ-ge-} &                   \obj{ɨ-ge-} &  \obj{u-gue-} / \obj{u-ge-} \\
\qu{bathe}   &    \rc{w-ipɨ-} &    \obj{w-ibɨ-} &     \obj{{\normalfont ∅}-ip-} &                  \obj{w-i-} \\
\qu{be-1}    &     \rc{w-ap-} &     \obj{w-ap-} &                             – &                \obj{w-awɨ-} \\
\qu{be-2}    &  \rc{w-et͡ʃi-} &  \obj{w-it͡ʃi-} &  \obj{{\normalfont ∅}-et͡ʃi-} &                  \obj{w-i-} \\
\qu{come}    &    \rc{w-epɨ-} &    \obj{w-ebɨ-} &                 \obj{k-arep-} &               \obj{k-əewɨ-} \\
\qu{go down} &   \rc{w-ɨptə-} &                 &                               &                             \\
\qu{go}      &   \rc{w-ɨdən-} &    \obj{w-ɨdo-} &                 \obj{k-aran-} &                 \obj{u-də-} \\
\mybottomrule
\end{tabular}
\end{table}

### 2023-08-23 documents/floats/ptirverbs.tex
fix abbrevs & lg names

\begin{table}
\centering
\caption[Verbs preserving \gl{1}\gl{s_a_} \rc{w-} in \PTir]{Verbs preserving \gl{1}\gl{s_a_} \rc{w-} in \PTir \parencites[292, 294, 339]{triomeira1999}[112-114]{meira1998proto}{meiraDBakuriyo}}
\label{tab:ptirverbs}
\begin{tabular}[t]{@{}llll@{}}
\mytoprule
{} &          \PTir &          \trio &                     \akuriyo \\
\mymidrule
\qu{go}   &  \rc{w-ɨtəmɨ-} &  \obj{wɨ-tən-} &                \obj{ə-təmɨ-} \\
\qu{say}  &    \rc{wɨ-ka-} &   \obj{wɨ-ka-} &                 \obj{wɨ-ka-} \\
\qu{come} &  \rc{w-əʔepɨ-} &  \obj{w-əepɨ-} &  \obj{{\normalfont ∅}-eepɨ-} \\
\qu{be-1} &      \rc{w-a-} &     \obj{w-a-} &     \obj{{\normalfont ∅}-a-} \\
\qu{be-2} &    \rc{w-eʔi-} &    \obj{w-ei-} &   \obj{{\normalfont ∅}-eʔi-} \\
\mybottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\centering
\caption[Verbs preserving \gl{1}\gl{sa} \rc{w-} in \PTir]{Verbs preserving \gl{1}\gl{sa} \rc{w-} in \PTir \parencites[292, 294, 339]{triomeira1999}[112-114]{meira1998proto}{meiraDBakuriyo}}
\label{tab:ptirverbs}
\begin{tabular}[t]{@{}llll@{}}
\mytoprule
{} &          \PTir &          \trio &                     \akuriyo \\
\mymidrule
\qu{go}   &  \rc{w-ɨtəmɨ-} &  \obj{wɨ-tən-} &                \obj{ə-təmɨ-} \\
\qu{say}  &    \rc{wɨ-ka-} &   \obj{wɨ-ka-} &                 \obj{wɨ-ka-} \\
\qu{come} &  \rc{w-əʔepɨ-} &  \obj{w-əepɨ-} &  \obj{{\normalfont ∅}-eepɨ-} \\
\qu{be-1} &      \rc{w-a-} &     \obj{w-a-} &     \obj{{\normalfont ∅}-a-} \\
\qu{be-2} &    \rc{w-eʔi-} &    \obj{w-ei-} &   \obj{{\normalfont ∅}-eʔi-} \\
\mybottomrule
\end{tabular}
\end{table}
